\chapter*{Abstract}
\phantomsection
\addcontentsline{toc}{chapter}{Abstract}

This book presents the design and implementation of a real-time \textbf{solar battery monitoring system} in a photovoltaic installation. The goal is to monitor and improve the efficiency of energy storage by providing accurate data on battery conditions, such as voltage, current, temperature, state of charge (SoC), and state of discharge (DoD).\\

The system relies on sensors to collect essential information from the batteries. This data is processed by a central unit and transmitted to a remote management platform. Analyzing this information allows for real-time decision-making, such as adjusting the charging or discharging of the batteries to prevent deterioration and extend their lifespan.\\

The operation of the system involves several key steps:
\begin{itemize}
	\item \textbf{Measuring Voltage and Current} : these two parameters are essential for monitoring battery health. Current helps determine the amount of energy entering or leaving the batteries, while voltage helps monitor charge levels and detect anomalies.
	\item \textbf{Coulomb Counting} : this method precisely calculates the state of charge (SoC) of the batteries by measuring the current entering and leaving over a given period.
	\item \textbf{State of Discharge (DoD)} : this parameter assesses the level of battery discharge, providing insights into the remaining energy and allowing for optimization of stored energy use.
	\item \textbf{Temperature Monitoring} : temperature variations affect battery performance and safety; monitoring temperatures helps prevent overheating.
	\item \textbf{Charge and Discharge Management} : by monitoring battery conditions, dynamic adjustments to charging and discharging cycles can optimize energy use.
	\item \textbf{Management Interface} : a user interface displays collected data and enables real-time monitoring of critical parameters, triggering alerts for issues such as overcharging, undervoltage, or overheating.
\end{itemize}

The ultimate goal of the system is to ensure \textbf{effective and safe management} of solar energy storage while maximizing battery lifespan and minimizing failure risks.\\

\textbf{Keywords} : solar batteries, monitoring, energy management, storage, optimization, SoC, DoD, photovoltaic system.
